Standalone Tactics using OpenTheory

### 2012-01-26 paper.tex
start work on section 2.1

\usepackage{url}
\usepackage{xspace}

@@

\subsection{\OpenTheory for Tactic Communication}
Introduction to article format.
Representing terms and proofs in the format.
Viewing tactics as derived inference rules.

>>>>

\usepackage{url,xspace,amssymb}

@@

\subsection{\OpenTheory for Tactic Communication}
The central concept in \OpenTheory is that of a \emph{theory package}, $\Gamma\rhd\Delta$, which proves that the set of theorems $\Delta$ logically derive from the set of assumptions $\Gamma$.
The basic unit\footnote{composite theory packages are also possible} for constructing theory packages is an \emph{article file}, which consists of instructions for a virtual machine whose operations include primitive inference rules of higher-order logic and basic term-manipulation.

<Intro to LCF kernel? Viewing tactics as derived inference rules?>

An article file represents a theory $\Gamma\rhd\Delta$.
As a special case, we can represent the proof of a single goal $g$ by taking $\Delta=\{\vdash g\}$.
More generally, by taking $\Delta$ to be the theorems proved by a tactic and $\Gamma$ to be any theorems the tactic uses, we can view the result of applying a tactic as a theory.

Furthermore, we can represent a higher-order logic term $t$ by the theory $\{\vdash\mathtt{K\;F\;}t\}\rhd\{\vdash\mathtt{K\;F\;}t\}$, where $\mathtt{K}:\alpha\to\beta\to\alpha$ is the combinator defined by $\mathtt{K}\;x\;y=x$, and $\mathtt{F}$ is falsity (any boolean would do).
The article format ensures $t$ is only written once in representing this theory.
This kind of encoding is necessary to represent terms of non-boolean type, since the conclusion of a theorem must be boolean.

Thus the same format, article files, can be used to encode terms and proofs for communication with tactics.
(Additional inputs and outputs can always be communicated separately.)
